---
title: "Shiny Application and Reproducible Pitch"
subtitle: "Heights of Fathers and Sons"
date: '2022-08-12'
output: slidy_presentation

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Project

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

Your Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.

2. Deploy the application on Rstudio's shiny server

3. Share the application link by pasting it into the provided text box

4. Share your server.R and ui.R code on github

## About the Project

- This project develops a tool to predict son's height from their father's.

- It uses Karl Peasons's data, which was influenced by Francis Galton's famous study

- The method is a simple linear regression

- The dataset ```father.son``` can be found in the ```UsingR``` package


## Summary of Data

```{r cars, echo = FALSE, message=FALSE}
library(UsingR)
galton <- father.son
colnames(galton) <- c("father", "son")
summary(father.son)
```

## Plot of Data

```{r pressure, echo=FALSE, message=FALSE, warning=FALSE}
model <- lm(son ~ father, data = galton)
plot(galton$father, galton$son, xlab = "Father's Height", main="Heights of Sons and Fathers (Inches)", 
             ylab = "Son's Height", bty = "o", pch = 16, col="grey60", height=50, width=50,
             xlim = c(55, 85), ylim = c(55, 85),
              
            
          abline(model, col = "darkblue", lwd = 2))
          abline(coef = c(0,1), type="l", lty=2)
```

## Links to the Project

-Github: https://github.com/jlpobrien/Developing-Data-Products-Project


-Shiny: https://jlpobrien.shinyapps.io/DevelopingDataProductsProject/



